Revision Memo for, ``Government Websites As Data: A methodological pipeline with application to the websites of municipalities in the United States''

### 2021-10-01 paper/jitp_rr_memo/jitp_rr2_memo.tex
typo
added sentence about scraping technique in our paper vs others to memo

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper. Thanks also to Reviewer 1 for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments s addressed in the order presented in the review.  We should note that we are now approximately 500 words over the 5,000 word limit. We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers. Of course, we are happy to trim further if necessary.  We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

	\textbf{Response}:  We removed the discussion of these studies from the conclusion. We added a brief paragraph to Section 2, in which we discuss the fact that researchers in other areas---beyond the analysis of government websites---have conducted computational content analyses of websites. We point to these studies as evidence that our pipeline will be applicable beyond the study of government websites.

>>>>

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper. Thanks also to Reviewer 1 for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments is addressed in the order presented in the review.  We should note that we are now approximately 500 words over the 5,000 word limit. We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers. Of course, we are happy to trim further if necessary.  We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

	\textbf{Response}:  We removed the discussion of these studies from the conclusion. We added a brief paragraph to Section 2, in which we discuss the fact that researchers in other areas---beyond the analysis of government websites---have conducted computational content analyses of websites. We point to these studies as evidence that our pipeline will be applicable beyond the study of government websites. The previous paragraph already explains that our methodology would improve the approaches in these studies by making it possible to use the same scraping technique for all websites being studied, rather than having to specify HTML tags for each site individually.
